---
title: "Analysis of Penguins Data using R"
author: "Lareina Lyu"
date: "2026-09-22"
---

In this blog, I will use R to compare flipper length across three penguin species from `palmerpenguins` dataset.

## Setup

- Load relevant packages.

```{r}
#| message: false
#| warning: false
library(palmerpenguins)
library(dplyr)
library(ggplot2)
```

## Cleaning the data

- Drop rows with missing values for further analysis.

```{r}
penguins_clean <- penguins |>
  filter(!is.na(flipper_length_mm))

head(penguins_clean, 5)
```

## Summary by species

- Calculate the number of penguins and their average flipper length for each species.

```{r}
penguins_clean |>
  group_by(species) |>
  summarise(
    count = n(),
    avg_flipper_mm = round(mean(flipper_length_mm), 1)
  )
```

## Visualizing flipper length

- @fig-flipper-length shows the distribution of flipper length for each species.
- **Findings**: The Gentoo penguins have the longest flipper length of the three species and Adelie penguins have the shortest.

```{r}
#| label: fig-flipper-length
#| fig-cap: "Flipper length of penguins by species."
#| warning: false
ggplot(penguins_clean, aes(x = species, y = flipper_length_mm, fill = species)) +
  geom_boxplot() +
  labs(x = "Species", y = "Flipper length (mm)") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Data

- Data: [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/),
Palmer Station Antarctica LTER.
The data are available under a
[CC-0](https://creativecommons.org/share-your-work/public-domain/cc0/) licence, in accordance with the
[Palmer Station LTER Data Policy](https://pallter.marine.rutgers.edu/data/)
and the [LTER Data Access Policy for Type I data](https://lternet.edu/data-access-policy/).

- Citation:
Horst AM, Hill AP, Gorman KB (2020).
palmerpenguins: Palmer Archipelago (Antarctica) penguin data.
R package version 0.1.0.
<https://allisonhorst.github.io/palmerpenguins/>.
doi: [10.5281/zenodo.3960218](https://doi.org/10.5281/zenodo.3960218).

## AI Usage Statement

I used Claude (Anthropic, Claude Opus 5.5) to assist with drafting part of the plotting code.